Output Summary

### 2023-04-05 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Use better x/y lims in post-v-prior plots

```{r mu_phi_O0_O1-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O0_O1[origin,pop]", prior_param = "mu_phi_O0_O1_pr",
                  origin = o_nor, xlim = c(0,1)
)
```

@@

```{r mu_psi_O1_nor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
                  origin = o_nor, xlim = c(0,1)
)
```

@@

```{r mu_psi_O1_hor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
                  origin = o_hor, xlim = c(0,1)
)
```

@@

```{r sig_lL_Pb-post-v-prior}
post_v_prior_pops(post_param = "sig_lL_Pb[pop]", prior_param = "sig_lL_Pb_pr[pop]",
                  xlim = c(0, 2)
)
```

@@

```{r sig_lDelta_L_Pb_Mb-post-v-prior}
post_v_prior_pops(post_param = "sig_lDelta_L_Pb_Mb[pop]", prior_param = "sig_lDelta_L_Pb_Mb_pr[pop]",
                  xlim = c(0, 2)
)
```

@@

```{r}
# set these figure options for all plots in this section
y_max = 0.2
xlim = c(-1,1)
knitr::opts_chunk$set(fig.width = 5, fig.height = 6)
```

>>>>

```{r mu_phi_O0_O1-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O0_O1[origin,pop]", prior_param = "mu_phi_O0_O1_pr",
                  origin = o_nor, xlim = c(0,1), y_max = 0.75
)
```

@@

```{r mu_psi_O1_nor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
                  origin = o_nor, xlim = c(0,1), y_max = 0.75
)
```

@@

```{r mu_psi_O1_hor-post-v-prior}
post_v_prior_pops(post_param = "mu_psi_O1[origin,pop]", prior_param = "mu_psi_O1_pr",
                  origin = o_hor, xlim = c(0,1), y_max = 0.75
)
```

@@

```{r sig_lL_Pb-post-v-prior}
post_v_prior_pops(post_param = "sig_lL_Pb[pop]", prior_param = "sig_lL_Pb_pr[pop]",
                  xlim = c(0, 1), y_max = 0.75
)
```

@@

```{r sig_lDelta_L_Pb_Mb-post-v-prior}
post_v_prior_pops(post_param = "sig_lDelta_L_Pb_Mb[pop]", prior_param = "sig_lDelta_L_Pb_Mb_pr[pop]",
                  xlim = c(0,1), y_max = 0.75
)
```

@@

```{r}
# set these figure options for all plots in this section
y_max = 0.15
xlim = c(-1,1)
knitr::opts_chunk$set(fig.width = 5, fig.height = 6)
```
